Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-05-03 Paper/main.tex
Changes in SS Tables and in Figures amountasked and con_overtime

\title{Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance.  All errors are ours.}}
\author{Joyce Sadka \and Enrique Seira  \and Christopher Woodruff }
\date{This draft:  20 January, 2017 \\[2 cm]}

@@

%#include
\begin{table}[H]
    \caption{Baseline Expectations}
    \label{Table_expectations}
    \begin{center}
       \scriptsize{\input{./Tables/SS_A.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:} 
    Summary stats of beliefs, total \& by type of (employee's) lawyer. First column displays beliefs without any conditioning, second columns conditions on knowing type of lawyer. Third and fourth columns of Panel B and C are condition on employee answering the survey so that comparison across is allowed.
    \textit{Do file: } \texttt{Table\_SS.do  Table\_SS\_bylawyer.do}
\end{table}

@@

\begin{landscape}
%#include
\begin{table}[H]
\caption{Determinants of overconfidence}
\label{Table_determinantsOC}
\begin{center}
\scriptsize{\input{./Tables/OC_reg.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very angry, and the scale is increasing. We use a measure of relative overconvidence which is the \textit{percentage} quantity expected over the calculators prediction.
\textit{Do file: } \texttt{oc\_reg.do oc\_reg\_B.do}
\end{table}

>>>>

\title{Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance.  All errors are ours.}}
\author{Joyce Sadka \and Enrique Seira  \and Christopher Woodruff }
\date{This draft:  \today \\[2 cm]}

@@

%#include
\begin{table}[H]
    \caption{Baseline Expectations}
    \label{Table_expectations}
    \begin{center}
       \scriptsize{\input{./Tables/SS_A.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:} 
    Summary stats of beliefs, total \& by type of (employee's) lawyer.
    \textit{Do file: } \texttt{Table\_SS.do  Table\_SS\_bylawyer.do}
\end{table}

\begin{table}[H]
    \caption{Baseline expectations comparison between parts}
    \label{Table_expectations_plaintiff_defendant}
    \begin{center}
       \scriptsize{\input{./Tables/SS_B.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:}

    \textit{Do file: } \texttt{Table\_SS\_bylawyer.do}
\end{table}

@@

\begin{landscape}
%#include
\begin{table}[H]
\caption{Determinants of overconfidence}
\label{Table_determinantsOC}
\begin{center}
\scriptsize{\input{./Tables/OC_reg.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use a measure of relative overconfidence which is the \textit{percentage} quantity expected over the calculators prediction.
\textit{Do file: } \texttt{oc\_reg.do oc\_reg\_B.do}
\end{table}
